target_offtarget

### 2025-07-08 manuscript_figures.Rmd
Swapped Figures S15 and 16

@@

#### Figure S15

@@

#### *** Final plot ***
```{r}
#PDF
ggsave("figures/manuscript_figure_2025/PDF/Figure_S15.pdf",
       width=12,
       height=7)

#PNG
ggsave("figures/manuscript_figure_2025/Png/Figure_S15.png",
       width=12,
       height=7)

@@

#### Figure S16
```{r, echo=FALSE, warning=FALSE, message=FALSE}

#PDF
ggsave("figures/manuscript_figure_2025/PDF/Figure_S16.pdf",
       width=12,
       height=7)

#PNG
ggsave("figures/manuscript_figure_2025/PNG/Figure_S16.png",
       width=12,
       height=7)
```

>>>>

### --------------------
#### Figure S15
```{r, echo=FALSE, warning=FALSE, message=FALSE}

#PDF
ggsave("figures/manuscript_figure_2025/PDF/Figure_S15.pdf",
       width=12,
       height=7)

#PNG
ggsave("figures/manuscript_figure_2025/PNG/Figure_S15.png",
       width=12,
       height=7)
```

@@

#### Figure S16

@@

#### *** Final plot ***
```{r}
#PDF
ggsave("figures/manuscript_figure_2025/PDF/Figure_S16.pdf",
       width=12,
       height=7)

#PNG
ggsave("figures/manuscript_figure_2025/Png/Figure_S16.png",
       width=12,
       height=7)

@@
